---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# jaspatial

<!-- badges: start -->
<!-- badges: end -->

The goal of jaspatial is to set up your environment to conduct geospatial analyses at January Advisors and provide 
a repository of common functions we have developed. 

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("januaryadvisors/jaspatial")
```
## Set up your environment

When you start a geospatial analysis, load the `jaspatial` library and then load all the other common geospatial packages and set the correct options:

```{r example}
library(jaspatial)
load_geo_packages() 
#This will load: sf, tigris, tidycensus, mapview, 
  #leaflet, leaflet.extras, leaflet.extras2, rmapshaper,
set_geo_options() #Set the correct options for tigris downloads
```

## Clean your data
You can also quickly clean and transform the projection of an sf object using `clean_shape`. The default projection that comes pre-loaded is `wgs84`. But you can use others, too.

```{r clean_shape}
clean_tx_counties <- clean_shape(tx_counties) #The default 

#Or change projection
utm14n <- st_crs("+proj=utm +zone=14 +ellps=GRS80 +datum=NAD83 +units=m +no_defs +towgs84=0,0,0")
clean_tx_counties_utm14n <- clean_shape(tx_counties, utm14n)
```


